---
title: "Data Wrangling Steps"
author: "Anthony Stachowitz"
date: "July 11, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(readxl)
```

### 1. Load dataset

This loads the individual datasets.   
```{r}
bosto_dataset_raw <- read_excel("C:/Users/Anthony/Desktop/R studio projects/boston/bosto_dataset_raw.xls")
```

### 3. Remove specific values

The Boston data set includes 14 variables. For my data analisis we are able to reduce the number of variable to down to 5.
```{r}
boston_wrangled <- bosto_dataset_raw[,c(1, 11:14)]
```

### 4. Change headers names to better reflect the data

There are some header names that are confusing and need to be more specific. I have changed the headers so that they are all consistent.
```{r}
names(boston_wrangled) <- c("Per Cap Crime", "Pupil-Teacher Ratio", "Proportion of African Americans", "Percent of Lower Status", "Median Home Value")
```

### 5. Check data set for NA's.

Check the data set for NA's. If there are NA's fill them in with the mean of the column.(No NA's were found)

```{r}
list_na <- colnames(boston_wrangled)[ apply(boston_wrangled, 2, anyNA) ]
list_na
```

